% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Portfolio Proposal} 

% Please do not change the subtitle
\subtitle{COMP320 Dissertation}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\abstract{}

\section{Notes:}
Which tree search technique performs best for different game catagories?

Comparison of the sample AI controllers in GVGAI. - Which perform best in which catagory of game?

Comparing game tree search techniques for general videogame AI (GVGAI)
PCG different game puzzles and see which tree search techniques perform the best in different areas.

Different search techniques:
Depth first search
MCTS
Breadth first search
Rolling horizon Evolutionary Algorithm 
MCTS/EA hybrid


Analysis of GVGAIs location, tracking where they spend most of their time in a level.
Analysis of GVGAI in a PCG level and figure out where they spend their time / where they die most often.

From that propose the two controllers that could work well as a hybrid?


\section{Research Questions:}
How does game tree search techniques compare for GVGAI?
Where does GVGAI succeed best in set games?
What are the most challenging areas for GVGAI in the GVGAI competition?
Where does each tree search technique do well in?(vague) 

Using game tree search techniques to compare the level difficulty for each game.
(Work out what techniques are good at some aspects of a game's level, and others are better at others.)




\end{document}